### 2025-09-25 paper/sec/introduction.tex
Contribs.

\paragraph{Contributions.} Our specific contributions are:

\begin{itemize}
\item A proof-of-concept LLM-based tool for iteratively transforming a preexisting opaque document and
associated data set into a transparent, data-driven counterpart;
\item An empirical evaluation of how well state-of-the-art models are able to solve the associated
interpretation and code synthesis problems.
\end{itemize}

We leave implementing a full Copilot-like authoring plugin for an IDE such as VSCode or Cursor for future
work.

>>>>

\paragraph{Contributions.} Our specific contributions are as follows. (\secref{conclusion:future-work}). We
leave implementing a full Copilot-like authoring plugin for an IDE such as VSCode or Cursor for future work.

\begin{itemize}
\item A proof-of-concept LLM-based tool for iteratively transforming a preexisting opaque document and
associated data set into a transparent, data-driven counterpart (\secref{authoring-workflow});
\item A summary of the natural language idioms we have studied (\secref{nl-idioms}) and an empirical
evaluation of how well state-of-the-art models are able to solve the associated interpretation and code
synthesis problems (\secref{evaluation}).
\end{itemize}
